### 2019-07-05 thesis-template/msc-thesis.tex
update

% Choose language
\newcommand{\setlang}[1]{\selectlanguage{#1}\nonfrenchspacing}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\source}[1]{\vspace{-3pt} \caption*{ Source: {#1}} }

\begin{document}

@@

{\large
\begin{tabular}[l]{ll}
Sebastian Bek\\
Matrikelnummer: & 3481802\\
Betreuer: & Prof. Filip Sadlo, Dr. Susanne Krömker\\
Datum der Abgabe: & 07.07.2019
\end{tabular}
}

@@

\section{Behaviour for Total Anisotropy}
\label{sect:total}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional Dirac-pulses as transmission profiles to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \caption*{TFLs and glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy1.png}
    \caption*{iteration $50$}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy2.png}
    \caption*{iteration $103$}
    \label{c)}
  \end{minipage}
\caption{intensity propagation in grid for total anisotropy}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite if presumed as perfect circle). Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter and escape each) as observable in Fig. \ref{anisotropy}. Nonetheless, the energies are transmitted in circular orbits around the circle center.	
\section{Energy Conservation Test}
\label{sect:conserve}
The energy conservation test was done in similar manner as thepropagation attenuation test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum (e.g. $\int_0^{2\pi}1\mathop{d\omega}=2\pi$) in iteration 0 in absolute values. This energetic error analysis yields the following graph depicted in Fig. \ref{energy}:

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/ftle_drain_alt.png}
    \caption*{LTG($0^\circ$)}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/drain_ftle_org.PNG}
     \caption*{FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
\caption{\enquote{drain} test field}
\label{drain_ftle_comp}
\end{figure}
We can observe the comparison between our invented FTLE-like approach and the one of Hlawatsch et al. in the depiction in Fig. \ref{drain_ftle_comp}. Note, that a sharper but weaker ridge is detected on the right side of the image, which shines similar to a cone shape from the top. We interpret the missing spot in the top center as an artifact stemming from the way we handle our light propagation, as we allow whole distributions of trajectories to be propagated (with a scalar attribute interpretable as propability). This causes a sampling drift, we already discussed in sect. \ref{sect:total}, leading to an energy distribution ending up outside of the field, for this position. The directive effect turns out to be not that strict and delayed compared to the classic tensor field line FTLE. The crucial difference is that the compared work of Hlawatsch et al. obtains the FTLE field from the gradient $\nabla\mathbf{\upvarphi}(\mathbf{x})$ of the flow map, which is in turn obtained from sampling of trajectories following tensor field lines. We will now capture the same comparison for the textbook example \enquote{double gyre}.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/gyre_ftle.png}
    \caption*{LTG($0^\circ$)}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/gyre_ftle_org.PNG}
     \caption*{FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
\caption{\enquote{gyre} test field}
\label{gyre_ftle_comp}
\end{figure}
Again, it is noticeable, that the results correspond to each other to a certain degree. This implies, that we obtained reasonable results generated by our method, but the classical tensor field line FTLE is more strict concerning its directive abilities and congruently does not do things by halves (like we do with our partitioned light distributions). We will now capture the star dataset revealing tensor field lines diverging in any direction from the center.

@@

Now, we will evaluate a classic textbook example called the \enquote{double gyre} \cite{shawn}, which is a quadruple gyre in our case for formatting reasons, yet yielding the same conceptual results. We compare the glyph representation to the LTG magnitude for a single slice ($0^\circ$) again:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[width=\textwidth]{img/gyre.png}
    \caption{\enquote{Gyre} test field}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle.PNG}
     \caption{LTG on \enquote{Gyre}($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle.PNG}
     \caption{FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
\label{gyre-ftle}
\end{figure}
We can observe the method segmenting ridges in local ROIs exhibiting diverging tensor field lines w.r.t. the $x$-axis ($0^\circ$). Note that even regions in antiparallel directions ridgres are detected to (literally) some degree: Remark the ridges being contiguos lines at the level of the gyre centers where converging turns into diverging. Also remember, that the resulting ridges are not to be concerned sharp ones, since we measure the separation of whole light distributions, which should be considered a continous response or measure. We again depict volume representations for this example:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre_volume2.png}
    \caption*{IsoVolume)}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_gauss_contour.PNG}
     \caption*{Contour}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_volume4.PNG}
     \caption*{GaussContour}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Gyre} test field}
\label{gyre_volume}
\end{figure}
When we consider the volumes for the \enquote{gyre} test field, we can remark the holes, which represent the gyres in the centers of the volume for a low and a high threshold, whereby we extract (filter out) the previously observed ridges in $3D$ for all directions $\omega$ simultaneously.

Now, that the approach has passed the textbook examples, we push it forward to be applied in real (measured) data to show its performance in discerning and segmenting ROIs from a human brain. The approach will detect LCS in the brain's tissue from MRI-measured diffusion tensors of a male subject at the age of 27. We compare ParaView's glyph representation to the FTLE method LTG for the test field \enquote{brain}:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[width=\textwidth]{img/brain_cyl_glyphs.PNG}
    \caption*{glyph representation}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/brain_ftle.PNG}
     \caption*{LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle_org.PNG}
     \caption*{FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Brain} test field}
\label{brain-ftle}
\end{figure}
Regarding Fig. \ref{gyre_volume}, we find that the approach detects the boundaries of concavities (lat.: Gyri) in the brain, forming the lobus cerebri (commonly known a lobes). The invented method could thus ,e.g. , aid to compute $3D$ models of a subject in medical sciences. It emphasizes regions with much flow-rate (throughput), because in this areas the anisotropy and/or tensor magnitude is increased, preventing the intensities from being absorbed, hence yielding to a high FTLE-response. The regions highlighted in red, are caused by high linear anisotropy measures, as we can infer from the glyph representation. Note that we do not show the volume representation in this case, since all directions (slices) look approximately the same because the tensor field is only introducing changes in tensor magnitude not in anisotropy as inferred from the glyph representation. The regions with a tensor magnitude higher than zero restrict the light propagation to certain areas with the constraint, that not all of the energy is absorbed by sorrounding cells in the local neighborhood. Again comparing the results to the classical FTLE on tensor field, we notice that the FTLE response is chaotic, since this MRI scan is subject to inherent MRI noise filling the background regions in the image. This noise produces random trajectories, leading to an increased gradient of the flow map and thus to a high FTLE response, as inferred from Fig. \ref{brain_ftle_comp}, which reveals trajectories running in random directions in background regions. Only in foreground regions, the trajectories are directed in definite manner, which is why the flow map's gradient is minimized along the brain structure (foreground, depicted in blue). Our approach uses absorption to get rid of noise present in the tensor field. Hence, we do not yield a noisy representation but a FG-BG segmented image, with red highlights in positions, where the tensor magnitude is maximized (and thus absorption is minimized). Remark, that the resulting volume does not inherently depend on the direction, because the test field does not introduce any strong linear anisotropy, as visible from the glyph representation. If no linear anisotropy was incorporated, the FTLE respons will also be independent on the direction to the greatest extent. The slices we obtain as our volume are, with reasonable explanation, more or less identical comparing them against each other for certain directions.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/brainDwnsmpl.png}
    \caption*{Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/brainDwnsmpl-TFL.PNG}
     \caption*{Hlawatsch's app.: TFLs}
    \label{b)}
  \end{minipage}
\caption{\enquote{brain} test field}
\label{brain_ftle_comp}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[width=\textwidth]{img/heart_org.PNG}
    \caption*{tensor magnitude}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/heart.PNG}
     \caption*{LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/heart_ftle_org.PNG}
     \caption*{Hlawatsch's app.}
    \label{b)}
  \end{minipage}
  \caption{\enquote{heart} test field}
\label{heart-ftle}
\end{figure}
After applying the LTG approach on the heart dataset, we observe the resulting FTLE-field, which is again not changing w.r.t. direction, which is why we do not show the volumes. The approach highlights the regions with diverging tensor field lines resulting from linear anisotropy or increased tensor magnitude, emerging as ridges. These ridges could now represent blood vessels and such. The red spot emphasized in the left of the image could, e.g., represent the highest diffusion velocity in tissue.
When considering the FTLE for the heart dataset depicted in Fig. \ref{heart-ftle}, we find that the trajectories exhibit strong correlations amongst them. This results from the low noise rate present in this dataset. The inital value for our angle is given by $0$ degree, which is why the trajectories follow this angle strictly in case of a zero matrix (corresponding to a noise free cell in background regions). In this case, we obtain the same results as the approach from Hlawatsch et al., whereas our global min-max normalization (due to noise) is becoming a redundant step for noiseless input data. A proof of this elaboration can be found in Fig. \ref{heart-ftle-comp}.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/heartDwnsmpl.png}
    \caption*{Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/heartDwnsmpl-TFL.PNG}
     \caption*{Hlawatsch's app.: TFLs}
    \label{b)}
  \end{minipage}
\caption{\enquote{heart} test field}
\label{heart-ftle-comp}
\end{figure}
Again considering the trajectories for the heart test field, we note that they all correlate in background regions, which causes the gradient of the flow map to equal zero. This occurs, since we do not have any MRI noise incorporated into the background of the field. Consequently, we obtain results corresponding to Hlawatsch's approach, which is in general susceptive to noise, but not in case the noise was removed or is not present at all initially. From observing Hlawatsch's approach detecting the heart edges, we can infer that the flow is also congruent inside of the heart, inducing a gradient response only to the edges. In our case, we have an offset response incorporated which happens even for total spherical isotropy, wherefore we will obtain a response even if the flow does not change locally (presumed it is not absorbed by low tensor magnitudes). This in turn stems from the fact, that we use a energetic flood-fill difference, which inherently introduces an offset response.

>>>>

% Choose language
\newcommand{\setlang}[1]{\selectlanguage{#1}\nonfrenchspacing}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\source}[1]{\vspace{-3pt} \caption*{ Source: {#1}} }
\setlength{\emergencystretch}{3em}
\begin{document}

@@

{\large
\begin{tabular}[l]{ll}
Sebastian Bek\\
Student ID: & 3481802\\
Supervisors: & Prof. Filip Sadlo, Dr. Susanne Krömker\\
Submission date: & 07.07.2019
\end{tabular}
}

@@

\section{Behaviour for Total Anisotropy}
\label{sect:total}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional Dirac-pulses as transmission profiles to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \caption*{TFLs and glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy1.png}
    \caption*{iteration $50$}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy2.png}
    \caption*{iteration $103$}
    \label{c)}
  \end{minipage}
\caption{intensity propagation in grid for total anisotropy}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite if presumed as perfect circle). Hence, the energy can never follow a perfect circle, but at best an octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter and escape each) as observable in Fig. \ref{anisotropy}. Nonetheless, the energies are transmitted in circular orbits around the circle center.	
\section{Energy Conservation Test}
\label{sect:conserve}
The energy conservation test was done in similar manner as thepropagation attenuation test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum (e.g. $\int_0^{2\pi}1\mathop{d\omega}=2\pi$) in iteration 0 in absolute values. This energetic error analysis yields the following graph depicted in Fig. \ref{energy}:

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/ftle_drain_alt.png}
    \caption*{LTG($0^\circ$)}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/drain_ftle_org_real.png}
     \caption*{FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
\caption{\enquote{drain} test field}
\label{drain_ftle_comp}
\end{figure}
We can observe the comparison between our invented FTLE-like approach and the one of Hlawatsch et al. in the depiction in Fig. \ref{drain_ftle_comp}. Note, that a sharper but weaker ridge is detected on the right side of the image, which shines similar to a cone shape from the top. We interpret the missing spot in the top center as an artifact stemming from the way we handle our light propagation, as we allow whole distributions of trajectories to be propagated (with a scalar attribute interpretable as propability). This causes a sampling drift, we already discussed in sect. \ref{sect:total}, leading to an energy distribution ending up outside of the field, for this position. The directive effect turns out to be not that strict and delayed compared to the classic tensor field line FTLE. The crucial difference is that the compared work of Hlawatsch et al. obtains the FTLE field from the gradient $\nabla\mathbf{\upvarphi}(\mathbf{x})$ of the flow map, which is in turn obtained from sampling of trajectories following tensor field lines.

@@

 We will now capture the star dataset revealing tensor field lines diverging in any direction from the center.
Now, we will evaluate a classic textbook example called the \enquote{double gyre} \cite{shawn}, which is a quadruple gyre in our case for formatting reasons, yet yielding the same conceptual results. We compare the glyph representation to the LTG magnitude for a single slice ($0^\circ$) again:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre.png}
    \caption*{a) Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{Gyre test field}
\label{gyre-ftle}
\end{figure}
We can observe the method segmenting ridges in local ROIs exhibiting diverging tensor field lines w.r.t. the $x$-axis ($0^\circ$). Note that even regions in antiparallel directions ridgres are detected to (literally) some degree: Remark the ridges being contiguos lines at the level of the gyre centers where converging turns into diverging. Again, it is noticeable, that the results correspond to each other to a certain degree. This implies, that we obtained reasonable results generated by our method, but the classical tensor field line FTLE is more strict concerning its directive abilities and congruently does not do things by halves (like we do with our partitioned light distributions). Also remember, that the resulting ridges are not to be concerned sharp ones, since we measure the separation of whole light distributions, which should be considered a continous response or measure. We again depict volume representations for this example:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre_volume2.png}
    \caption*{a) IsoVolume}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_gauss_contour.PNG}
     \caption*{b) Contour}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_volume4.PNG}
     \caption*{c) GaussContour}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Gyre} test field}
\label{gyre_volume}
\end{figure}
When we consider the volumes for the \enquote{gyre} test field, we can remark the holes, which represent the gyres in the centers of the volume for a low and a high threshold, whereby we extract (filter out) the previously observed ridges in $3D$ for all directions $\omega$ simultaneously.

Now, that the approach has passed the textbook examples, we push it forward to be applied in real (measured) data to show its performance in discerning and segmenting ROIs from a human brain. The approach will detect LCS in the brain's tissue from MRI-measured diffusion tensors of a male subject at the age of 27. We compare ParaView's glyph representation to the FTLE method LTG for the test field \enquote{brain}:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/brain_cyl_glyphs.PNG}
    \caption*{a) glyph representation}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Brain} test field}
\label{brain-ftle}
\end{figure}
Regarding Fig. \ref{gyre_volume}, we find that the approach detects the boundaries of concavities (lat.: Gyri) in the brain, forming the lobus cerebri (commonly known a lobes). The invented method could thus, e.g., aid to compute $3D$ models of a subject in medical sciences. It emphasizes regions with increased change in flow-rate (throughput), because in this areas the anisotropy and/or tensor magnitude is increased, preventing the intensities from being absorbed, hence yielding to a high FTLE-response. The regions highlighted in red, are caused by high tensor magnitudes, as we can infer from the glyph representation revealing no linear anisotropy at all. Note that we do not show the volume representation in this case, since all directions (slices) look approximately the same because the tensor field is only introducing changes in tensor magnitude not in anisotropy as inferred from the glyph representation. The regions with a tensor magnitude higher than zero restrict the light propagation to certain areas with the condition, that not all of the energy is absorbed by sorrounding cells in the local neighborhood. Again comparing the results to the classical FTLE (Hlawatsch's approach) on tensor fields in Fig. \ref{brain_ftle_comp}, we notice that the FTLE response is chaotic, since this MRI scan is subject to inherent MRI noise filling the background regions in the image. This noise produces random trajectories, leading to an increased gradient of the flow map and thus to a high FTLE response, which reveals trajectories running in random directions in background regions. Only in foreground regions, the trajectories are directed in definite manner, which is why the flow map's gradient is minimized along the brain structure (foreground, depicted in blue in Fig \ref{brain_ftle_comp} c)). Yet, our approach uses absorption to decrease noise present in the tensor field and reasonable min-max scaling to conduct $100\%$ of the intensity for the cell with the highest tensor magnitude. Hence, we do not yield a noisy representation but a FG-BG segmented image, with red highlights in positions, where the tensor magnitude is maximized (and thus absorption is minimized). Remark, that the resulting volume does not inherently depend on the direction, because the test field does not introduce any strong linear anisotropy, as visible from the glyph representation in Fig. \ref{brain_ftle_comp} a). If no linear anisotropy was incorporated, the FTLE response will also be independent on the direction to the greatest extent. The slices we obtain as our volume are, with reasonable explanation, more or less identical comparing them against each other for certain directions.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/brainDwnsmpl.png}
    \caption*{a) Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/brainDwnsmpl-TFL.PNG}
     \caption*{b) Hlawatsch's app.: TFLs}
    \label{b)}
  \end{minipage}
\caption{\enquote{brain} test field}
\label{brain_ftle_comp}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[width=\textwidth]{img/heart_org.PNG}
    \caption*{a) tensor magnitude}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/heart.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth]{img/heart_ftle_org.PNG}
     \caption*{c) Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{heart} test field}
\label{heart-ftle}
\end{figure}
After applying the LTG approach on the heart dataset, we observe the resulting FTLE-field, which is again not changing w.r.t. direction, which is why we do not show the volumes. The approach highlights the regions with diverging tensor field lines resulting from linear anisotropy or increased tensor magnitude, emerging as ridges. These ridges could now represent blood vessels and such. The red spot emphasized in the left of the image could, e.g., represent the highest diffusion velocity in tissue.
When considering the FTLE for the heart dataset depicted in Fig. \ref{heart-ftle}, we find that the trajectories exhibit strong correlations amongst them. This results from the low noise rate present in this dataset. The inital value for our angle is given by $0$ degree, which is why the trajectories follow this angle strictly in case of a zero matrix (corresponding to a noise free cell in background regions). In this case, we obtain the same results as the approach from Hlawatsch et al., whereas our global min-max normalization (due to noise) is becoming a redundant step for noiseless input data. A proof of this elaboration can be found in Fig. \ref{heart-ftle-comp}.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=0.9\textwidth]{img/heartDwnsmpl.png}
    \caption*{Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=0.9\textwidth]{img/heartDwnsmpl-TFL.PNG}
     \caption*{Hlawatsch's approach: TFLs}
    \label{b)}
  \end{minipage}
\caption{\enquote{heart} test field}
\label{heart-ftle-comp}
\end{figure}
Again considering the trajectories for the heart test field, we note that they all correlate in background regions, which causes the gradient of the flow map to equal zero. This occurs, since we do not have any MRI noise incorporated into the background of the field. Consequently, we obtain results corresponding to Hlawatsch's approach, which is in general susceptive to noise, but not in case the noise was removed or is not present at all initially. From observing Hlawatsch's approach detecting the heart edges, we can infer that the flow is also congruent inside of the heart, inducing a gradient response only to the edges. In our case, we have an offset response incorporated which happens even for total spherical isotropy, wherefore we will obtain a response even if the flow does not change locally (presumed it is not absorbed by low tensor magnitudes). This in turn stems from the fact, that we use a energetic flood-fill difference, which inherently introduces an offset response.
